NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-30 paper/evaluation.tex
remove test

\section{Evaluation and Feedback}
%\shusen{discussed feedback and comment about the proposed system}

The initial motivation for designing the proposed tool is driven by the error analysis challenges faces by NLP researchers working on the natural language inference task. We work closely with two NLP experts, and their constant evaluation and feedback have guided the design and development process.
%
However, since the two NLP experts are heavy involved in the design process, they may be blinded for the potential problems of the tool due to familiarity.  In order to undercover the limitation and identify areas for improvements we gathered a wider audience from both visualization (4 researchers include 3 PhD student and one Postdoc Researcher) and NLP background (5 PhD students who are familiar with the concept of natural language inference and attention) for the evaluation of the tool.  
%

>>>>

\section{Evaluation and Feedback}

The initial motivation for designing the proposed tool is driven by the error analysis challenges faces by NLP researchers working on the natural language inference task. We work closely with two NLP experts, and their constant evaluation and feedback have guided the design and development process.
%
However, since the two NLP experts are heavy involved in the design process, they may be blinded for the potential problems of the tool due to familiarity.  In order to undercover the limitation and identify areas for improvements we gathered a wider audience from both visualization (4 researchers include 3 Ph.D. level student and one postdoc researcher) and NLP background (5 Ph.D. level students who are familiar with the concept of natural language inference and attention) for the evaluation of the tool.

### 2018-03-30 paper/predSummary.tex
re-arrange figure
space squeeze
remove test

\subsection{Summary View}
\label{sec:allPairs}
% outline:
%  - how to identify the sensitivity of pairs
We can focus on only one individual example at a time for a detailed analysis using the combination of all previously discussed views. As a result, how to select a pair of sentences of interest from the development or test dataset, which consists of close to $10k$ examples, is an obvious challenge.
% - what is the interesting pairs
In addition, the experts are also interested in obtaining a high-level understanding beyond the information the prediction accuracy provides of the behavior of the $10k$ sentence pairs.
%
These two goals are the two sides of the same coin, the selection task will become much easier if we can generate a good visual summary of the $10k$ examples that help experts obtain a deeper understanding of the whole $10k$ examples.

@@

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{summaryView}
 \caption{
Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
%
The user can select the treemap to focus on the specific type of scenarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
The selection can be further narrowed down by selecting the bin in the histogram.
In (c) and (d), each point corresponds to one prediction.
 }
\label{fig:summaryView}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{summaryView}
 \vspace{-6mm}
 \caption{
Summarize the prediction results and sensitivity of the entire development set, and provide an explorative interface to select an example of interest.
We summarize all the prediction results in (a), where the green block indicates correct predictions, the orange block indicates wrong predictions, and the label (e.g., E/E, E/N) indicates the ground truth label and the predicted label (N-Neural, E-Entailment, C-Contradiction).
%
The user can select the treemap to focus on the specific type of scenarios and reveal the histogram (b) and scatterplot (c) for displaying per-pair information on the selected subset.
The selection can be further narrowed down by selecting the bin in the histogram.
In (c) and (d), each point corresponds to one prediction.
 }
 \vspace{-2mm}
\label{fig:summaryView}
\end{figure}

\subsection{Summary View}
\label{sec:allPairs}
% outline:
%  - how to identify the sensitivity of pairs
We can focus on only one individual example at a time for a detailed analysis using the combination of all previously discussed views. As a result, how to select a pair of sentences of interest from the development dataset, which consists of close to $10k$ examples, is an obvious challenge.
% - what is the interesting pairs
In addition, the experts are also interested in obtaining a high-level understanding beyond the information the prediction accuracy provides of the behavior of the $10k$ sentence pairs.
%
These two goals are the two sides of the same coin, the selection task will become much easier if we can generate a good visual summary of the $10k$ examples that help experts obtain a deeper understanding of the whole $10k$ examples.

@@
